---
title: "World Development Indicators"
author: "Brandon Akinseye, Zeke Bickham, Freddy Garcia, Carlos Gonzalez, Gabriel Gray, Kevin Yu"
date: "`r Sys.Date()`"
output: github_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE,  
                      warning = FALSE, message = FALSE, 
                      fig.align = "center",
                      R.options = list(max.print=100))
```

## Project Description


## Project Goals
The goals of this project are to analyze the relationships between various world development indicators across the years for all countries. We hope to gain more insight into factors that affect the quality of life in a country as well as how countries have developed through the past few decades.

## Link to Dataset
https://databank.worldbank.org/source/world-development-indicators

## Dataset Information
The World Bank DataBank contains time series data on many different topics for each country in the world. The World Development Indicators dataset contains metrics about global development through various themes (e.g. poverty and inequality, people, environment, economy, states and markets, and global links). The data is compiled from officially-recognized international sources and contains 1,400 time series indicators for 217 economies and more than 40 country groups, with data for many indicators going back more than 50 years.

## Visualizations

```{r visualization_num1}
library(readr)
library(tidyverse)
library(dplyr)

wdi_data <-read_csv("~/SDS 322E/final_project/Project_Data_1.csv", show_col_types = FALSE)

wdi_data %>%
  filter(`Time` == "2015", `GDP per capita (current US$) [NY.GDP.PCAP.CD]` != "..") %>%
  mutate(GDPperCapita = as.numeric(`GDP per capita (current US$) [NY.GDP.PCAP.CD]`)) %>%
  ggplot(aes(x = GDPperCapita)) +
  geom_histogram() +
  xlab("GDP per Capita (current USD)") +
  ylab("Count") +
  ggtitle("Distribution of GDP per Capita for Countries in 2015")
```
---
```{r visualization_num2}
wdi_data %>%
  filter(`Time` == "2018",
         `Life expectancy at birth, total (years) [SP.DYN.LE00.IN]` != "..",
         `Current health expenditure (% of GDP) [SH.XPD.CHEX.GD.ZS]` != "..") %>%
  mutate(LifeExpectancy = as.numeric(`Life expectancy at birth, total (years) [SP.DYN.LE00.IN]`),
         HealthExpend = as.numeric(`Current health expenditure (% of GDP) [SH.XPD.CHEX.GD.ZS]`)) %>%
  ggplot(aes(x = HealthExpend, y = LifeExpectancy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  xlab("Current Health Expenditure (% of GDP)") +
  ylab("Life Expectancy at Birth (years)") +
  ggtitle("Life Expectancy versus Health Expenditure for Various Countries in 2018")
```

## Hypotheses
1. If a country spends more on healthcare, then their population will live healthier lives.

## References

The following is a link to The World Bank DataBank:
https://databank.worldbank.org/source/world-development-indicators